Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-19 pkg/disttree/inst/draft/rejoinder.Rnw
Z updates -> please re-read
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2339 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: a6f5c0c53c028af27844d28645e082498d06eed2

\documentclass[american,foldmarks=false,noconfig]{uibklttr}
%\documentclass{article}
\usepackage{sfmath,hyperref,color,enumitem,soul}
%% additional style file to include bibliograph in class uibklttr
%\usepackage{letterbib}
%\usepackage{natbib,hyperref}

@@

\makeatletter
\@setplength{refvpos}{75mm}
\makeatother
\setlength{\textheight}{25cm}
\definecolor{quotecolor}{rgb}{0.4,0.4,0.5}

\newenvironment{reto}{
    \begin{color}{uibkorange}
    \textbf{Reto:~}
        \itshape
}{
    \end{color}
}

\definecolor{fixmecol}{rgb}{1,1,0.7}
\newcommand{\fixme}[1]{{\sethlcolor{fixmecol}\hl{#1}}}

\usepackage{amsmath}

\begin{document}
\SweaveOpts{concordance=TRUE}
\begin{letter}{
Nicoleta Serban\\
Area Editor\\
The Annals of Applied Statistics}

\setkomavar{subject}{Revision of AOAS1804-015: Distributional 
regression forests for probabilistic precipitation forecasting 
in complex terrain}

@@

Thank you very much for the constructive and helpful feedback from you, 
the associate editor and the two referees. The manuscript has been 
improved and additional results haven been obtained from further evaluations.

The most important changes are:
\begin{itemize}

\item The evaluations performed for all 95 observation stations 
in the main manuscript have been carried out under different 
distribution assumptions for 15 observation stations in order to 
test for robustness against distributional misspecifications. 
Results are provided in an online supplement 
(Supplement 1: Different Response Distributions) 
which comes with our revised manuscript.

\item The more extensive evaluations for station Axams have been 
carried out for 14 other observation stations. Results are 
provided in an online supplement (Supplement 2: Stationwise Evaluation)
which comes with our revised manuscript. As this also contains
the results that were presented in Appendix B we have removed this
section of the appendix.

\item The mathematical notation in Appendix A is now more precise.

\item In the calculation of variable importance we have detected some inconsistencies.
Thus, we have revised the applied method to evaluate this measurement and recalculated
variable importance for the distributional forest.

@@

\vspace*{-2.8cm}
\hspace*{-0.3cm}signature %\includegraphics{zeileis-signature}

@@

The required size of the training data heavily depends on the complexity 
of the model, however, in different applications where we have tested the 
distributional forest it performed quite well with at least 50 observations. \\
Applying the Law of Large Numbers it can be shown that random forests do not overfit, 
not even for an increasing number of trees (Breiman 2001, Hastie et al. 2001, 
Biau et al. 2016). Therefore, it is recommended to build forests with a large number 
of trees as this generally yields more accurate predictions. 
However, ``[\dots] the computational cost for inducing a forest increases linearly 
with the number of trees, so a good choice results from a trade-off between 
computational complexity and accuracy'' (Biau et al. 2016, p.~205). Following this 
advice, we decided to build forests consisting of 100 trees.\\
Moreover, Hastie et al. (2001, p.~596) recommend to build trees of maximal depth:
``Our experience is that using full-grown trees seldom costs much, and 
results in one less tuning parameter.''
Thus, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) and \texttt{alpha} 
(the significance level for the statistical tests in the tree algorithm) should 
be kept rather low. However, in a distributional framework it also has to be 
considered that the minimal number of observations in a node needs to be high 
enough in order to allow for estimating the distribution parameters reasonably well.
In our application we have set \texttt{minsplit} to 50 and \texttt{minbucket} to 20.
These tuning parameters are now also listed in the main manuscript in Sections~3.2.
and discussed in Section~4.

@@

We apologize for the confusion the missing equation numbers 
might have caused. They are now added.

@@

We have measured fitting time and prediction time for our 
application. For single predictions the distributional forest 
can keep up with the other models. However, as you already 
stated correctly, each prediction made by the forest is based 
on an observation-specific weight matrix and therefore has to 
be calculated separately. For that reason prediction time for a 
set of observations is clearly higher for the forest model than 
the GAMLSS models or the EMOS. The exact results and times can 
be found in Supplement 2 (Stationwise Evaluation).

\begin{review}
abstract: the acronym 'GAMLSS' should be spelled out the first 
time it is used
\end{review}

We have rephrased this part of the abstract now spelling out 'GAMLSS' at 
its first appearance.

\begin{review}
p3: I'm not sure if people outside the weather forecasting 
community is familiar with the notion of an 'ensemble', so 
this should be explained briefly
\end{review}

@@

\begin{review}
p7: What is meant by 'domain knowledge'?
\end{review}

We have rephrased this as 'expert knowledge in the application domain'
in Section~2.2.

@@

The residual QQ plots (Dunn et al. 1996) illustrate the probability 
integral transform (PIT, Gneiting et al. 2007) values of the observations 
in the testing data and are therefore scale invariant. A more detailed 
explanation can be found in Supplement 2 (Stationwise Evaluation).

@@

This seems to result from the one specific training and validation period 
(training: 1985--2008, validation: 2009-2012).
The advantages of the GAMLSS model even out at most of the stations when looking 
on the results of a cross-validation. We have extended Section~4 to discuss this 
issue. The results of an extended evaluation including a cross-validation for a 
set of $15$ stations can be found in Supplement 2 (Stationwise Evaluation).

@@

You are right, our explanation was incorrect, thank you for pointing
this out! We have now clarified that the model employs a censored
distribution but the observations are not censored, just non-negative
with a point mass at zero.

@@

We have rephrased this part of the caption to ``Observations are non-negative 
and modeled by a Gaussian distribution left-censored at zero.
The observations are depicted by crosses and the predicted point mass
from the model by filled circles.'' to clearly distinguish between the model
and the observations.

@@

For each new observation $z$ the corresponding 
parameter vector $\hat{\Theta}(z)$ can be calculated following 
the given formula. But you are right, one can also just evaluate 
the predicted terminal node for $z$ if the predicted parameter
vector for this node is already known as there is one unique 
parameter vector for all observations in the same terminal node.
This is now also explained at the end of Section~2.2.

@@

Yes, in the forest model the parameter vector has to be estimated 
separately for each new prediction as it is based on an 
observation-specific weight matrix. For that reason, making 
predictions for a set of new observations is clearly more 
time consuming for the forest model than the GAMLSS models 
or the EMOS model. However, the time needed to make one single 
prediction is similar for all methods. The exact results 
concerning fitting and prediction times can now be found in
Supplement 2 (Stationwise Evaluation).

@@

This is itself a complex topic with an own scientific community
focusing on the development and improvement of numerical weather
forecasts. Bauer, Thorphe, and Brunet (2015) give a good overview
of the history and open scientific challenges of NWP ensemble forecast
models including a discussion about unresolved processes and possible
solutions beyond the current state of NWP models.
We have added this reference next to the statement you are referring to.

The following figure shows a comparison of the true local topography
(Robinson et~al. 2014; left)
and the model topography of the GEFS reforecast model
($0.5^\circ \times 0.5^\circ$, approx. $50 \times 50~km^2$; right) to illustrate
the extent of simplification needed in such global weather forecast models.

@@

As stopping criteria the minimal number of observations to perform 
a split (\texttt{minsplit}) is set to 50, the minimal number of 
observations in a terminal node (\texttt{minbucket}) is set to 20 
and the significance level for variable selection (\texttt{alpha}) 
is kept at the default value 1. We have added this information in 
the manuscript in Section~3.2, 'Distributional forest', and
also discussed the choice of these tuning parameter in Section~4 and
in the answer to the second point of the associate editor.

@@

@@

Apologies for the unclear notation in Appendix A.
Depending on whether the split variable $Z_l$ is a numeric 
or a categorical variable, $t_l$ is either a
$k$~-~or~$k \cdot H$~-~dimensional vector.
We have revised the corresponding parts in the manuscript (also 
regarding your comments 17--20) and we hope that it now clarifies 
the content.

@@

As in the foregoing point this was just a general notation, but 
actually the variables corresponding to the $l$-th split variable 
are considered, i.e. $t_l$, $\mu_l$ and $\sigma_l$. Thank you for
pointing this out, the missing indices have been added in the
appendix of the manuscript.

@@

Yes, one stopping criterion is that no p-value is beneath the 
selected significance level. Therefore, no further 
split is performed in the considered node in this case.

@@

Thank you very much for your feedback and helpful suggestions. We hope 
the improvements we made on the paper can clear your doubts and concerns.

@@

We have applied a Gaussian distribution left-censored at zero
as it has proven to be an adequate choice for this type of 
application in earlier publications.
Moreover, the residual QQ plots and PIT histograms illustrate
that the models are well calibrated employing this distribution.
But thank you very much for the advice to consider a hurdle model!
This is definitely a good idea and therefore we have carried out the
same evaluations as presented in the paper but employing a
Gaussian hurdle model. Additionally, a logistic distribution 
left-censored at zero has been applied as well in the same setting in
order to account for heavier tails. The results of these evaluation
can be found in Supplement 1 (Different Response Distributions). 
Overall, the distributional forest is proven to be very robust against 
distributional misspecifications. Therefore, we decided to keep the 
distributional assumption considered in the main manuscript but we have 
also discussed the tested alternatives in Section~4.

@@

As you mention one way to deal with skewness is to use a distribution
with an additional skewness parameter (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016) which increases the complexity of the statistical
models.
Another frequently used approach is to apply a
power-transformation (Stidd 1973, Hutchinson 1998, Stauffer et al. 2017) to
remove the majority of the skewness from the data. The optimal transformation
depends on the application and data set, in our case we are following the work
of Stauffer et al. (2017) who presented a similar application on the very same
data set. As our results show (Figure~3 in the manuscript) this approach works 
well for the application presented in our manuscript.
Moreover, the focus of this paper is on the features of the presented
distributional forest regarding variable selection and the capability
to also model non-linear effects rather than optimizing the model
specification for this particular application.

%The skewness results from the characteristics of precipitation sums. 
%Most of the time no or only moderate precipitation amounts are forecasted 
%and observed. In some situations (e.g., days with thunderstorms, cold and 
%warm fronts, \dots) large amounts of precipitation can be observed at 
%specific sites. This is often also depict by the ensemble prediction 
%system where a subset of all members predicts rather large amounts 
%(compared to the overall ensemble mean or median). This yields strongly 
%skewed ensemble forecasts which has to be addressed in some sort.\\
%\fixme{\textit{FIXME: Should this explanation why there is skewness be included?}}

%As you mention one way how to deal with skewness would be to 
%apply a distributional family with an additional parameter to capture
%skewness. However, this can be very complex and thus lead to less well 
%fitting estimators of the location and scale parameter.
%Moreover, the focus of this paper is on the features of the presented 
%distributional forest regarding variable selection and the capability 
%to also model non-linear effects rather than optimizing the model 
%specification for this particular application.
%Transforming the data to remove large parts of the skewness is
%a frequently used approach. Therefore, employing such a transformation 
%allows for a better way of comparing our results to those presented in 
%literature. In this study we are thus following Stauffer et al. (2017) 
%using the power transformation which turned out to be optimal 
%for a similar application for the very same study area.

@@

We completely agree with you as that other models such as
GAMLSS are clearly advantageous regarding interpretability.
These models provide a very powerful framework that works
well in a wide range of applications and research fields,
including meteorology. Therefore, our intention is not to present
distributional forests as a replacement of these commonly used methods
but rather as a well working alternative. Especially if one is mainly
interested in predictive skill and a good performing fully automated
weather forecasting tool the interpretability is not implicitly needed
in some cases (machine learning performance vs. interpretability, e.g.,
Rasp and Lerch 2018).
We adapted our manuscript as we want to emphasize that in our
application the focus is mainly on the predictive performance and less on
the interpretation of the different effects.
We hope we could point this out clearly. \\
\fixme{\textit{FIXME: Where should this be pointed out in the manuscript? 
In the discussion or after introducing trees and forests? (trade-off between
flexibility of the model and interpretability)}}

@@

We apologize for the confusion the missing equation numbers 
might have caused. They are now added.
We have also rephrased Section~2.3. which now first introduces random 
forests and then distributional forests as an extension of classical 
random forests.

\begin{review}
5. In the introduction it is said that ``while requiring no 
expert knowledge for the model specification''. I do not think 
it is true given that the authors do not consider a possible 
distributional misspecification at all. In addition, If I am 
not wrong, the functional forms in the distributional 
regression models do not have to be prespecified. Applying a 
mixed model type representation it should be possible to
have for instance interaction surfaces separated into the pure 
interaction effects and the main effects. For instance, 
Wood et al. (2013) discuss a generic approach for defining 
well-identified and interpretable effect decompositions in 
tensor product interactions again based on the mixed model 
representation of penalised model components, while Goicoa 
et al. (2017); Ugarte et al. (2017) determine the identifiability
constraints from the null space of the penalties associated 
with the spatio-temporal interaction effect.
\end{review}

Thank you for your suggestions and the references. These are all
good ideas, however, in our application the number of covariates
is too large in order to keep a model with all interactions manageable.
We have also discussed this in Section~4 of the main manuscript and
rephrased the corresponding sentence in the introduction to ``while 
requiring no meteorological knowledge about the atmospheric processes 
which drive formation of precipitation for the model specification.'' 
in order to clarify that this refers only to the variable prespecification 
in this application.

\begin{review}
6. A simulation study designed according to the data set should 
be used in order to give an empirical evidence that the random 
forests are generally better able to perform predictions compared 
to the competing methods. The figures indicate that advantages 
for the chosen station are rather minor and one should keep in 
mind that GAMLSS and boosting yield interpretable results which 
the random forests do not do. also, what happens when choosing 
another station than Axams? The figure 8 indicates that the 
distributional forest does not perform better in all stations 
and I am wondering whether a meteorologist would really do a 
better job on a relative scale of precipitation.
\end{review}

In order to investigate on these questions we have carried out the full
analysis as presented for station Axams in the main manuscript for 14
further observation stations. It shows that the distributional
forest is very robust against distributional misspecifications
and almost always competitive with the best among the other methods 
or even better. The exact results are provided in 
Supplement 2 (Stationwise Evaluation) and discussed in Section~4. 
Especially for meteorologists intending to apply model output 
statistics (MOS) for several hundreds of observation stations 
(e.g., Wahl 2014, Rasp and Lerch 2018)
the distributional forest provides a good and robust alternative. 
Even though computational costs are higher than for an EMOS model, 
they are similar as for a prespecified model and lower than for 
a model applying variable selection based on cross-validation.
Execution times have been measured and can be found
in Supplement~2 (Stationwise Evaluation).

\begin{review}
7. How are the folds chosen for performing the predictions? 
is it 4 subsequent years or randomly chosen 4 years out of 
the 28? I expect this to have a strong impact on the predictions 
and sensitivity with respect to this needs to be considered both 
in simulations and the real study.
\end{review}

The folds of the cross-validation are chosen randomly. The data 
set of 28 years is split randomly into 7 blocks of 4 years which 
are not necessarily successive. This is now also explained in the 
description of the cross-validation setup third paragraph of 
Section~3.3.

We have chosen two different setups: First we learned the model
on the first 24 years and evaluated on the following 4 years
in order to provide a classic time ordered setup. 
However, no influence of time is to be expected which is also supported by 
an autocorrelation coefficient of -0.007 of the out-of-bag quantile 
residuals of the distributional forest model for station Axams for
a time lag of 1 day.
% ## calculation of autocorrelation:
% load("Axams_24to4.rda") 
% set.seed(4)
% pdf <- predict(Axams_24to4$df, newdata = Axams_24to4$testdata, type = "parameter")
% pit_df <- cbind(0, pnorm(Axams_24to4$testdata[,"robs"], mean = pdf$mu, sd = pdf$sigma))
% pit_df[Axams_24to4$testdata[,"robs"]>0, 1] <- pit_df[Axams_24to4$testdata[,"robs"]>0, 2]
% ac <- acf(qqrplot(pit_df)$residuals)
To evaluate the models in a broader framework a cross-validation 
with the above described choice of folds was applied. The results
for station Axams are included in the main manuscript, results
for 14 additional stations can be found in
Supplement~2 (Stationwise Evaluation).

@@

As mentioned in our response to your comment 5, and also discussed in Section~4, 
the high number of covariates (80) restricts the possibilities of variable 
selection and model specification. For an AIC or BIC based selection an 
evaluation of 80 main effects for two parameters would make this a very complex
procedure. Moreover, Hofner et al. (2016, p.~3) stated that the 
AIC-based variable selection methods implemented in the \textsf{R} 
package \textbf{gamlss} ``[...] can be unstable, especially when it comes 
to selecting possibly different sets of variables for 
multiple distribution parameters.'' For that reason we decided
not to apply such a selection method.

@@

By a `basic EMOS' we are referring to the linear distributional 
regression model based on the idea presented by Gneiting et al. (2005) 
applying a left-censored at zero Gaussian distribution where only the 
ensemble mean is included for the location parameter and the ensemble 
standard deviation for the scale parameter.
We now introduce the model which we are referring to as a `basic EMOS'
in detail in the main manuscript in the first paragraph of Section~3.

\begin{review}
Third, why not to include interactions in the boosting algorithm 
as well? this should be conceptually straight forward? 
\end{review}

Including only pairwise interactions
of the 80 available variables would already lead to 3160 additional
covariates which would make the model too complex and hardly manageable
regarding computational costs. Therefore, we decided not to include
any interactions in the boosting algorithm.
This issue is now addressed and discussed in Section~4.
% factorial(80)/factorial(80-2)/factorial(2)

\begin{review}
Fourth, why are 100 trees chosen in the forest? Is this a a default 
value? May this number not also be dependent on the complexity of 
the model? Why not to choose the number of trees similar to what is 
done in boosting? this would also increase the computation time of 
the forest a lot.
\end{review}

>>>>

\documentclass[american,foldmarks=false,noconfig]{uibklttr}
\usepackage{amsmath,sfmath,hyperref,color,enumitem,soul}

@@

\makeatletter
\@setplength{refvpos}{68mm}
\makeatother
\setlength{\textheight}{25cm}
\definecolor{quotecolor}{rgb}{0.4,0.4,0.5}

\definecolor{fixmecol}{rgb}{1,1,0.7}
\newcommand{\fixme}[1]{{\sethlcolor{fixmecol}\hl{\textit{FIXME: #1}}}}

\begin{document}

\begin{letter}{
Nicoleta Serban\\
Area Editor\\
The Annals of Applied Statistics}

\setkomavar{subject}{Revision of AOAS1804-015}

@@

Thank you very much for the constructive and helpful feedback from you, 
the associate editor, and the two referees. Based on this feedback, the
manuscript has been revised and embellished with additional results
from further evaluations. We feel that this substantially improved our
contribution.
%
The most important changes are:
\begin{itemize}

\item \emph{Supplement 1: Different response distributions.}\\
To assess the appropriateness and robustness of the distributional
assumption (censored Gaussian) made in the main manuscript, further
response distributions (two-part Gaussian hurdle; censored
logistic) are evaluated to potentially better capture lower
and upper tails, respectively. The supplement follows the
evaluations performed for all 95 observation stations 
in the main manuscript using all three response distributions
for a subset of 15 stations.

\item \emph{Supplement 2: Stationwise evaluation.}\\
The show that the more extensive cross-validation results -- obtained only
for one station (Axams) in the main manuscript -- are fairly typical,
they are extended to 14 other observation stations. This also incorporates
results that were previously presented in Appendix B which has consequently
been omitted from the main manuscript.

\item \emph{Section~4: Discussion.}\\
The concluding section of the main manuscript has been rewritten and
extended to regarding discussion of: variable selection, tuning parameters,
distributional specifications (referring to Supplement~1), and regional
differences (referring to Supplement~2).

\item \emph{Appendix~A: Tree algorithm.}\\
The exposition has been extended and embellished, in particular regarding
mathematical notation.

% \item In the calculation of variable importance we have detected some inconsistencies.
% Thus, we have revised the applied method to evaluate this measurement and recalculated
% variable importance for the distributional forest.

@@

% \vspace*{-2.8cm}
% \hspace*{-0.3cm} %\includegraphics{zeileis-signature}

@@

The required size of the training data heavily depends on the complexity 
of the underlying effects. However, in different applications we have tested the 
distributional forest performed quite well starting from about 50--100 observations.

Applying the Law of Large Numbers it can be shown that random forests do not overfit 
as the number of trees increases (Breiman 2001, Hastie et al.\ 2001, 
Biau et al.\ 2016). Therefore, in principle, forests can be built with a very
large number of trees as this cannot deteriorate the predictions.
However, ``[\dots] the computational cost for inducing a forest increases linearly 
with the number of trees, so a good choice results from a trade-off between 
computational complexity and accuracy'' (Biau et al.\ 2016, p.~205). Following this 
advice, we decided to build forests consisting of 100 trees. Increasing this number
further would not change the results much.

Moreover, Hastie et al.\ (2001, p.~596) recommend to build trees of maximal depth:
``Our experience is that using full-grown trees seldom costs much, and 
results in one less tuning parameter.''
Thus, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) should be kept low
-- but in our context large enough for estimating the distribution parameters
reasonably well. Thus, in our application we have set \texttt{minsplit} to 50 and
\texttt{minbucket} to 20. The significance level \texttt{alpha} (for early stopping
upon non-significance) is set to 1, thus disabling any early stopping.
These tuning parameters are now also listed in the main manuscript in Sections~3.2.
and discussed in Section~4.

@@

We apologize for the confusion that the missing equation numbers 
have caused. They have now been added.

@@

We have measured fitting time and prediction time for our 
application. For observation-by-observation predictions -- as
done in real-time -- the computational cost for the distributional
forest is comparable to the GAMLSS approaches. The former have
to re-fit the model using the observation-specific weights
while the latter has to set up the model matrices for all the
additive terms. However, when predicting a set of observations
the costs for the GAMLSS are lower (due to leveraging matrix
operations) and for the distributional forest higher (as it
still operates observation-wise) but not prohibitively so.
The exact results and times can be found in Supplement 2
(Stationwise Evaluation).

\begin{review}
abstract: the acronym `GAMLSS' should be spelled out the first 
time it is used
\end{review}

We have rephrased this part of the abstract now spelling out
`GAMLSS' more explicitly at its first appearance.

\begin{review}
p3: I'm not sure if people outside the weather forecasting 
community is familiar with the notion of an `ensemble', so 
this should be explained briefly
\end{review}

@@

\begin{review}
p7: What is meant by `domain knowledge'?
\end{review}

We have rephrased this to `expert knowledge in the application domain'
in Section~2.2.

@@

The residual QQ plots (Dunn et al.\ 1996) are built on top of
the probability integral transform (PIT, Gneiting et al.\ 2007).
Therefore they are invariant to transformations that preserve
the PIT, as is the case here. A more detailed 
explanation can be found in Supplement 2 (Stationwise Evaluation).

@@

This seems to result from the one specific training and validation period 
(training: 1985--2008, validation: 2009-2012) and from East Tyrol having
somewhat different weather than the rest of Tyrol.

The advantages of the GAMLSS model even out at most of the stations when looking 
on the results of a cross-validation. We have extended Section~4 to discuss this 
issue. The results of an extended evaluation including a cross-validation for a 
set of $15$ stations can be found in Supplement 2 (Stationwise Evaluation).

@@

You are right, our explanation was incorrect, thank you for pointing
this out. We have now clarified that the \emph{model} employs a censored
distribution while the \emph{observations} are not censored, just non-negative
with many ties at zero.

@@

We have rephrased this part of the caption to ``Observations are non-negative 
and modeled by a Gaussian distribution left-censored at zero.
The observations are depicted by crosses and the predicted point mass
from the model by filled circles.'' to clearly distinguish between the
\emph{model} and the \emph{observations}.

@@

For each new observation $z$ the corresponding 
parameter vector $\hat{\Theta}(z)$ can be calculated following 
the given formula. But you are right, this is equivalent to simply
obtaining the paramter vector that has been estimated in the 
corresponding node when learning the tree. This is now also
explained at the end of Section~2.2.

@@

Yes, in distributional forests the parameter vector has to be estimated 
separately for each new prediction as it is based on
observation-specific weights. For that reason, making 
predictions for \emph{a set of} new observations is more 
time consuming for the forest (where predictions are obtained
separately) than the GAMLSS models (where matrix operations
can be leveraged). However, when making predictions observation
by observation -- as done in real-time -- the time required is
comparable for the forest and GAMLSS. The exact results 
regarding fitting and prediction times can now be found in
Supplement 2 (Stationwise Evaluation).

@@

A reference to Bauer, Thorphe, and Brunet (2015) has been added. They
give a good overview of the history and open scientific challenges
of NWP ensemble forecast models including a discussion about
unresolved processes and possible solutions beyond the current state
of NWP models.

To illustrate the issue in our forecast domain,
the following figure shows a comparison of the true local topography
(Robinson et~al. 2014; left)
and the model topography of the GEFS reforecast model
($0.5^\circ \times 0.5^\circ$, approx. $50 \times 50~km^2$; right). 
This conveys the extent of topographical simplification needed in
such global weather forecast models.

@@

As stopping criteria the minimal number of observations to perform 
a split (\texttt{minsplit}) is set to 50, the minimal number of 
observations in a terminal node (\texttt{minbucket}) is set to 20 
and early stopping (or ``pre-pruning'') based on the significance level is disabled
(by setting \texttt{alpha} to 1). We have added this information in 
the manuscript in Section~3.2, `Distributional forest', and
also discussed the choice of these tuning parameter in Section~4 and
in the answer to the second point of the associate editor.

@@

\fixme{This reply needs to be rewritten. It should be listed first
which variables correspond to each other between the models. Then
you can explain that the greater variation in the forest is not
surprising. Finally, it should be pointed out where in the manuscript
this is also discussed.}

@@

Apologies for the unclear notation in Appendix~A.
Depending on whether the split variable $Z_l$ is a numeric 
or a categorical variable, $t_l$ is a vector either of
dimension $k$ or $k \cdot H$.
We have revised the corresponding parts in the manuscript (also 
regarding your comments 17--20) and hope that these aspects
are now conveyed clearly.

@@

As in the previous point this was just a general notation, but 
actually the variables corresponding to the $l$-th split variable 
are considered, i.e. $t_l$, $\mu_l$ and $\sigma_l$. Thank you for
pointing this out, the missing indices have been added in the
appendix of the manuscript.

@@

Yes, significance can be used as one of the stopping criteria,
so that partitioning is stopped early upon non-signifcance
of the tests. This is sometimes also called ``pre-pruning'' in
the tree literature.

However, in our applications pre-pruning is disabled which
is explained in \dots \fixme{Improve Appendix~A to better
reflect this. Also align with the other comments about
alpha.}

@@

Thank you very much for your feedback and helpful suggestions. We hope 
the improvements we made address your doubts and concerns.

@@

Thank you for emphasizing this issue. In the initial submission
we did include assessments of calibration by graphical means
(QQ plots and PIT histograms). But we completely agree that a
more thorough assessment of the distributional specification is
preferable in this context.

Therefore, we followed your advice and considered both a different
distribution for the continuous part and a two-part hurdle model.
For the former, the logistic distribution (also left-censored at zero)
is used as it has heavier tails and was previously used in the
precipitation forecasting literature \fixme{add reference}.
For the latter, a two-part model is used combining a binary
zero hurdle ($y = 0$ vs.\ $y > 0$) and an adjusted Gaussian distribution
(left-truncated at zero).

We have carried out the
same evaluations as presented in the main manuscript and present
the full results in Supplement 1 (Different Response Distributions). 
The main insights from this are also discussed in Section~4:
At most stations the censored Gaussian manuscript from the main
manuscript performs at least as well as the two alternative
distributions, if not better. Moreover, the distributional forest
proves to be rather robust against distributional misspecifications.
Therefore, the discussion in the main manuscript is still based
on the censored Gaussian distribution.

@@

Our manuscript follows the frequently-used approach of applying a
power-transformation (Stidd 1973, Hutchinson 1998, Stauffer et al.\ 2017)
to be more easily comparable to previous publications in the field.
These focus on predicting location and scale based on mean and
variance from the NWP ensemble. Hence, we also follow that approach
but adopt a different strategy for estimating selecting variables
and estimating nonlinear effects and interactions.

As you correctly point out, another way to deal with skewness is to
use an extended distributional specification (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016). This increases the complexity of the statistical
models and makes the comparison to publications based on power transformations
more difficult. Therefore, we feel that this exceeds the scope of this
contribution but we do discuss it in Section~4 as being of interest for
future research. \fixme{Include one or two sentences about this as an
outlook in the discussion of distributional specifications.}

@@

We completely agree with you that GAMLSS are tremendously useful,
especially in situations where an interpretable but still
well-performing model is needed. The intention of our work is not
to present distributional forests as a replacement of GAMLSS but
rather as a complementing technique for the distributional regression
toolbox. Much like random forests and GAMs are complements in
the conditional mean regression toolbox.

In this sense, distributional forests are appealing for weather
forecasting tasks because the focus is not so much on interpretation
but often much more on: (a)~forecasting skill and (b)~(semi-)automatic
application of models on a larger domain. See also the discussion
in, e.g., Rasp and Lerch 2018).

We have adapted our manuscript to reflect that we focus on forecasting
skill in a large number of models -- and not so much on interpretation.

\fixme{Where should this be pointed out in the manuscript? 
Z: Both in the introduction when the ``zoo'' of regression techniques
is introduced -- and again in the discussion (possibly along with
variable selection?).}

@@

We apologize for the confusion that the missing equation numbers 
have caused. They have now been added.
We have also rephrased Section~2.3. which now first introduces random 
forests and then distributional forests as an extension of classical 
random forests.

\begin{review}
5. In the introduction it is said that ``while requiring no 
expert knowledge for the model specification''. I do not think 
it is true given that the authors do not consider a possible 
distributional misspecification at all. In addition, If I am 
not wrong, the functional forms in the distributional 
regression models do not have to be prespecified. Applying a 
mixed model type representation it should be possible to
have for instance interaction surfaces separated into the pure 
interaction effects and the main effects. For instance, 
Wood et al.\ (2013) discuss a generic approach for defining 
well-identified and interpretable effect decompositions in 
tensor product interactions again based on the mixed model 
representation of penalised model components, while Goicoa 
et al.\ (2017); Ugarte et al.\ (2017) determine the identifiability
constraints from the null space of the penalties associated 
with the spatio-temporal interaction effect.
\end{review}

Thank you for your suggestions and the references. Indeed we did
not discuss sufficiently the possibilities for including interactions
in GAMLSS. This has been remedied, see Section~4.

However, in our application the number of covariates is too large
(80) to even consider all pairwise interactions (3160 combinations)
using the approaches mentioned above, let alone interactions of higher orders.

We now discuss this in Section~4 of the main manuscript and
rephrased the corresponding sentence in the introduction to ``while 
requiring no meteorological knowledge about the atmospheric processes 
which drive formation of precipitation for the model specification'' 
in order to clarify that this pertains to the variable selection.

\begin{review}
6. A simulation study designed according to the data set should 
be used in order to give an empirical evidence that the random 
forests are generally better able to perform predictions compared 
to the competing methods. The figures indicate that advantages 
for the chosen station are rather minor and one should keep in 
mind that GAMLSS and boosting yield interpretable results which 
the random forests do not do. Also, what happens when choosing 
another station than Axams? The figure 8 indicates that the 
distributional forest does not perform better in all stations 
and I am wondering whether a meteorologist would really do a 
better job on a relative scale of precipitation.
\end{review}

In order to investigate these questions we have carried out the full
analysis as presented for station Axams in the main manuscript for 14
further observation stations. It shows that the distributional
forest is very robust against distributional (mis)specifications
and almost always competitive with the best among the other methods 
or even better. The exact results are provided in 
Supplement 2 (Stationwise Evaluation) and discussed in Section~4. 
Especially for meteorologists intending to apply model output 
statistics (MOS) for dozens or hundreds of observation stations 
(e.g., Wahl 2014, Rasp and Lerch 2018)
the distributional forest provides a good and robust alternative. 
Computational costs are clearly higher than for a basic EMOS model, 
but similar to a prespecified GAMLSS and lower than for GAMLSS
using variable selection by cross-validation. Fitting and forecasting
times are reported now in Supplement~2 (Stationwise Evaluation).

Regarding forecasting tasks other than the one presented in
the manuscript, we would \emph{not} expect that distributional
forests are \emph{``generally better''}. As for (boosted) GAMs and
random forests we would expect that sometimes (boosted) GAMLSS and
sometimes distributional forests perform better. As already argued
above we see the methods as complements not substitutes.

\fixme{Refer again to the corresponding point in the manuscript.}

\begin{review}
7. How are the folds chosen for performing the predictions? 
Is it 4 subsequent years or randomly chosen 4 years out of 
the 28? I expect this to have a strong impact on the predictions 
and sensitivity with respect to this needs to be considered both 
in simulations and the real study.
\end{review}

The folds of the cross-validation are chosen randomly. The data 
set of 28 years is split randomly into 7 blocks of 4 years which 
are not necessarily successive. This is now also explained in the 
description of the cross-validation setup in the third paragraph of 
Section~3.3. As already argued previously, the same cross-validation
approach is not only applied to Axams but also 14 further stations
in Supplement~2 to check for robustness across stations.

In addition to the cross-validation setup there is also the setup
where models are learned on the first 24 years and evaluated on the
final 4 years. Thus, the classic time-ordered setup is employed there,
again for Axams and 14 further stations.

Moreover, no influence of time is to be expected as autocorrelations of
daily lags are typically very low. For example, the autocorrelation
coefficient of the out-of-bag quantile residuals from the distributional
forest for station Axams is only $-0.007$.
% ## calculation of autocorrelation:
% load("Axams_24to4.rda") 
% set.seed(4)
% pdf <- predict(Axams_24to4$df, newdata = Axams_24to4$testdata, type = "parameter")
% pit_df <- cbind(0, pnorm(Axams_24to4$testdata[,"robs"], mean = pdf$mu, sd = pdf$sigma))
% pit_df[Axams_24to4$testdata[,"robs"]>0, 1] <- pit_df[Axams_24to4$testdata[,"robs"]>0, 2]
% ac <- acf(qqrplot(pit_df)$residuals)

@@

As mentioned in our response to your comment 5 above (and now also discussed in Section~4),
the high number of covariates (80) prevents simply including all variables
(or even all interactions) without further penalization. For an AIC- or BIC-based selection an 
evaluation of 80 main effects for both distributional parameters would make this a very complex
procedure. Moreover, Hofner et al.\ (2016, p.~3) stated that the 
selection methods implemented in the \textsf{R} 
package \textbf{gamlss} ``[...] can be unstable, especially when it comes 
to selecting possibly different sets of variables for 
multiple distribution parameters.'' For that reason we considered
the boosting-based approach as an alternative approach to variable selection
in GAMLSS.

@@

By a `basic EMOS' we are referring to the idea of Gneiting et al.\ (2005)
that employs a distributional regression with linear predictors for
location and scale, respectively, based on the corresponding empirical
mean and variance from the NWP ensemble.
We now introduce the model which we are referring to as a `basic EMOS'
in detail in the main manuscript in the first paragraph of Section~3.

\begin{review}
Third, why not to include interactions in the boosting algorithm 
as well? This should be conceptually straight forward? 
\end{review}

As argued above, including only pairwise interactions
of the 80 available variables would already lead to 3160 additional
covariates which would make the model even more complex and substantially
increase (the already high) computational costs. Therefore, we decided not to include
any interactions in the boosting algorithm which is now addressed and
discussed in Section~4.
% choose(80, 2)

\begin{review}
Fourth, why are 100 trees chosen in the forest? Is this a default 
value? May this number not also be dependent on the complexity of 
the model? Why not to choose the number of trees similar to what is 
done in boosting? This would also increase the computation time of 
the forest a lot.
\end{review}
